---
title: "An Anlysis of CO2 Emission"
author: "Ye Li"
date: "1/17/2020"
output: html_document
---

```{r setup, include=FALSE}
#load needed R packages for data analysis and R Markdown
knitr::opts_chunk$set(echo = TRUE)

require(tidyverse)

```

## Introduction

This is a mini-report to analyze and visualize the **EDGAR CO2 emissions 1970-2016** dataset. The dataset is downloaded from the GitHub repository at <https://github.com/openclimatedata/edgar-co2-emissions> on January 23, 2020. 

The dataset was originally reported in Crippa, M., Oreggioni, G., Guizzardi, D., Muntean, M., Schaaf, E., Lo Vullo, E., Solazzo, E., Monforti-Ferrario, F., Olivier, J.G.J., Vignati, E., Fossil CO2 and GHG emissions of all world countries - 2019 Report, EUR 29849 EN, Publications Office of the European Union, Luxembourg, 2019, ISBN 978-92-76-11100-9, [https://doi.org/10.2760/687800, JRC117610.](https://doi.org/10.2760/687800, JRC117610.)


More about the dataset and similar climate datasets can be found at <https://openclimatedata.net/>

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks and results within the document. 


```{r import, echo=FALSE}



```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
