---
title: "An Anlysis of CO2 Emission"
author: "Ye Li"
date: "1/17/2020"
output: html_document
---

```{r setup, include=FALSE}
#load needed R packages for data analysis and R Markdown
knitr::opts_chunk$set(echo = TRUE)

require(tidyverse)

```

## Introduction

This is a mini-report to analyze and visualize the **EDGAR CO2 emissions 1970-2016** dataset. The dataset is downloaded from the GitHub repository at <https://github.com/openclimatedata/edgar-co2-emissions> on January 23, 2020. 

The dataset was originally reported in Crippa, M., Oreggioni, G., Guizzardi, D., Muntean, M., Schaaf, E., Lo Vullo, E., Solazzo, E., Monforti-Ferrario, F., Olivier, J.G.J., Vignati, E., Fossil CO2 and GHG emissions of all world countries - 2019 Report, EUR 29849 EN, Publications Office of the European Union, Luxembourg, 2019, ISBN 978-92-76-11100-9, [https://doi.org/10.2760/687800, JRC117610.](https://doi.org/10.2760/687800, JRC117610.)


More about the dataset and similar climate datasets can be found at <https://openclimatedata.net/>

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks and results within the document. 


## Data

Here are the first few rows of the dataset. 
```{r import, echo=FALSE}

# import data from the downloaded data file 
# note the relative path for importing the data
CO2Em <- read.csv("../data/edgar-co2-emissions.csv")

head(CO2Em)

```

It contains columns **`r colnames(CO2Em)`**. They are the country code, country Name, cateogrical sectors, year of CO2 emission was calculated, and the emission in kilotons (kt). The categorical sectors include `r levels(CO2Em$Sector)`.

The unit kilotons for the Emission column was not noted in the original dataset. We added the unit to the column name as **Emissions_kt** and saved the new dataset under the *data_derived* subfolder. 

```{r renamecol, echo = FALSE}
# change the column name of Emissions to include the unit kt
CO2Em_kt <- CO2Em
colnames(CO2Em_kt)[5] <- "Emissions_kt"

#write the new dataframe into a csv file under data_derived

write.csv(CO2Em_kt, "../data_derived/CO2Emission_kt.csv", row.names = FALSE)

```


## Carbon Dioxide emissions from different sectors in the U.S.

We can filter out data for the United States and plot them in the following figure. 

```{r plotEm, echo=FALSE, fig.show='asis'}

#filter out US data and plot them

CO2EM_US_plot <- ggplot(data = CO2Em[CO2Em$Code == 'USA', ], aes(x = Year, y = Emissions, color = Sector)) +
  geom_point() +
  ggtitle("Emissions of Carbon Dioxide from different sectors in the U.S.
          ") +
  labs( y = "Emissions (kt)") +
  theme_classic() +
  theme(legend.title = element_blank()) 
  
  
ggsave("../figures/CO2Em_US.png")

CO2EM_US_plot

```

## How significant are the changes over the years in the U.S.

```{r plotEm_box, echo=FALSE, fig.show='asis'}

#filter out US data and plot them

CO2EM_US_Boxplot <- ggplot(data = CO2Em[CO2Em$Code == 'USA', ], aes(x = Sector, y = Emissions, color = Sector)) +
  geom_boxplot() +
  ggtitle("Emissions of Carbon Dioxide from different sectors in the U.S.
          ") +
  labs( y = "Emissions (kt)") +
  coord_flip() +
  theme_classic() +
  theme(legend.position = "none") 
  
ggsave("../figures/CO2Em_US_Boxplot.png")

CO2EM_US_Boxplot

```


